---
output:
  pdf_document: default
  html_document: default
---
## Importing libraries
```{r}
library(stats)
library(dplyr)
library(ggplot2)
library(ggfortify)
library(cluster)
library(readr)
library(factoextra)
```

## Load the dataset
```{r}
data1 <- read.csv("Customersdata.csv")

```

## Data Preprocessing
```{r}
# Sub-setting of only numerical type of data columns from the data set
data <- data1 %>% select(Channel, Region, Age, Fresh, Milk, Grocery, Frozen, Detergents_Paper,
                         Delicatessen, Annual.Income..k..)
```

## Preprocessed dataset
```{r}
# Printing of the top 3 rows of preprocessed dataset
head(data, n=3) 
```

## Setting seed
```{r}
set.seed(1)# Setting seed 1 as a random number
```

## Implementing of K Means Clustering Algorithm for clustering the customer
```{r}
# Implementing K-means clustering with k=6
KMC = kmeans(data,6)
```

## Plotting of K means clustering
```{r}
# cluster plotting of K Means Clustering
autoplot(KMC,data,frame=TRUE)
```

## Evaluation of K means clustering
```{r}
#Evaluating K means clustering
eval(KMC)
```

## Implementing of Hierarchical Clustering Algorithm
```{r}
# Implementing of hierarchical clustering in proprocessed dataset
hcluster <- hcut(data, k = 6, stand = TRUE)
```

## Plotting of hierarchical clustering using a dendogram
```{r}
# Plotting for the hierarchical clustering
fviz_dend(hcluster, show_labels = FALSE, rect = TRUE, cex =0.5)
```

## Evaluation of Hierarchical clustering
```{r}
#Evaluating Hierarchical clustering
eval(hcluster)
```

